Preventing Runtime Errors of Redis at Compile Time

### 2015-11-20 paper.tex
ready to go

\begin{minted}[xleftmargin=1em]{haskell}
newtype Popcorn p q a = Popcorn { unPopcorn :: Redis a }

@@

\begin{minted}[xleftmargin=1em]{haskell}
del :: KnownSymbol s
    => Proxy s
    -> Popcorn xs (Del xs s) (Either Reply Integer)
del key = Popcorn $ Hedis.del (encodeKey key)
\end{minted}

@@

\begin{minted}[xleftmargin=1em]{haskell}
encodeKey :: KnownSymbol s => Proxy s -> ByteString
encodeKey = encode . symbolVal
\end{minted}

@@

\subsection{Denoting containers}
Most Redis commands only work with a certain type of these containers. To
 annotate what container a key is associated with, we introduce these container
 types.

@@

incrbyfloat :: (KnownSymbol s, Get xs s ~ Just (StringOf Double))
     => Proxy s -> Double -> Popcorn xs xs (Either Reply Double)
incrbyfloat key n = Popcorn $ Hedis.incrbyfloat (encodeKey key) n
\end{minted}

@@

\begin{minted}[xleftmargin=1em]{haskell}
llen :: (KnownSymbol s, Get xs s ~ Just (ListOf x))
        => Proxy s
        -> Popcorn xs xs (Either Reply Integer)
llen key = Popcorn $ Hedis.llen (encodeKey key)
\end{minted}

@@

Users may need to make assertions about the status of some key-type bindings in
 a Redis program. For example, declaring the existence of a key and the type
 of its associating value. We provide these functions, which do nothing but
 fiddling with types.

@@

-- empty precondition
start :: Popcorn ’[] ’[] ()
start = Popcorn $ return ()
\end{minted}

@@

\begin{minted}[xleftmargin=1em]{haskell}
main :: IO ()
main = do
    conn <- connect defaultConnectInfo
    result <- runRedis conn $ unPopcorn $ start
        `bind` \_ ->  declare
                        (Proxy :: Proxy "A")
                        (Proxy :: Proxy Integer)
        `bind` \_ ->  incr     (Proxy :: Proxy "A")
        `bind` \n ->  case n of
            Left  err -> lpush (Proxy :: Proxy "L") 0
            Right n   -> lpush (Proxy :: Proxy "L") n
        `bind` \_ ->  lpop     (Proxy :: Proxy "L")
    print result
\end{minted}

@@

\begin{minted}[xleftmargin=1em]{haskell}
(>>>) :: IMonad m => m p q a -> m q r b -> m p r b

program = start
    >>> declare
            (Proxy :: Proxy "A")
            (Proxy :: Proxy Integer)
    >>> incr    (Proxy :: Proxy "A")
    >>> lpush   (Proxy :: Proxy "L") 0
    >>> lpop    (Proxy :: Proxy "L")
\end{minted}

\section{Discussions}
\paragraph{Syntax}
No one could ignore the glaring shortcoming of the syntax, which occurs mainly
 in two places: \emph{symbol singletons} and \emph{indexed monad}. We are hoping
 that these issues could be solved with future syntactic extensions.

@@

All other data structures in Redis also follow the semantics similar to
 "List or nothing" as \mintinline{text}{LLEN} has. Take the case of
 \mintinline{text}{GET}, which has a similar semantics that should be typed:

@@

Some command may take a variable number of arguments as inputs, and returns more
 than one value as outputs. To illustrate this, consider
 \mintinline{haskell}{sinter} in \mintinline{haskell}{Hedis}:

@@

Notice that \textbf{not all Hedis programs can be typechecked} (even if they
 might turn out to be type safe). We opted for type safety instead of
 expressiveness.

@@

Redis also provides \emph{transactions}, another context for executing commands.
Redis transactions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served \textbf{in the middle}.\footnotemark In contrast, we cannot make such
 a guarantee in the ordinary context, which may destroy the assertions we made
 in types.

@@

We have demonstrated how a DSL with variable-bindings could be embedded in types.
With more and more extensions added to the language, Haskell is gradually
 becoming a dependently-typed language,\footnote{Why not be dependently typed? \url{http://stackoverflow.com/questions/12961651/why-not-be-dependently-typed}}
 but it's not that dreadful as many (including us) would have thought.

>>>>

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
newtype Popcorn p q a = Popcorn { unPopcorn :: Redis a }

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
del :: KnownSymbol s
    => Proxy s
    -> Popcorn xs (Del xs s) (Either Reply Integer)
del key = Popcorn $ Hedis.del (encodeKey key)
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
encodeKey :: KnownSymbol s => Proxy s -> ByteString
encodeKey = encode . symbolVal
\end{minted}

@@

\subsection{Denoting containers}
Most Redis commands only work with a certain type of these containers. To
 annotate what container a key is associated with, we introduce these types for
 the universe of containers.

@@

incrbyfloat :: (KnownSymbol s
    , Get xs s ~ Just (StringOf Double))
    => Proxy s
    -> Double
    -> Popcorn xs xs (Either Reply Double)
incrbyfloat key n =
    Popcorn $ Hedis.incrbyfloat (encodeKey key) n
\end{minted}

@@

\begin{minted}[xleftmargin=1em]{haskell}
llen :: (KnownSymbol s
      , Get xs s ~ Just (ListOf x))
     => Proxy s
     -> Popcorn xs xs (Either Reply Integer)
llen key =
     Popcorn $ Hedis.llen (encodeKey key)
\end{minted}

@@

Users may need to make assertions about the status of some key-type bindings in
 a Redis program. Specifically, when declaring or renouncing the existence of
 a key and the type of its associating value. We provide these functions,
 which do nothing but fiddle with types.

@@

-- to be used at the beginning of a program
start :: Popcorn ’[] ’[] ()
start = Popcorn $ return ()
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
main :: IO ()
main = do
    conn <- connect defaultConnectInfo
    result <- runRedis conn $ unPopcorn $ start
        `bind` \_ ->  declare
                        (Proxy :: Proxy "A")
                        (Proxy :: Proxy Integer)
        `bind` \_ ->  incr     (Proxy :: Proxy "A")
        `bind` \n ->  case n of
            Left  err -> lpush (Proxy :: Proxy "L") 0
            Right n   -> lpush (Proxy :: Proxy "L") n
        `bind` \_ ->  lpop     (Proxy :: Proxy "L")
    print result
\end{minted}

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
(>>>) :: IMonad m => m p q a -> m q r b -> m p r b
\end{minted}
\begin{minted}[xleftmargin=1em]{haskell}
program = start
    >>> declare
            (Proxy :: Proxy "A")
            (Proxy :: Proxy Integer)
    >>> incr    (Proxy :: Proxy "A")
    >>> lpush   (Proxy :: Proxy "L") 0
    >>> lpop    (Proxy :: Proxy "L")
\end{minted}

\section{Discussions}
\paragraph{Syntax}
No one could ignore the glaring shortcoming of the syntax, which occurs mainly
 in two places: \emph{symbol singletons} and \emph{indexed monad}. We are hoping
 that these issues could be resolved with future syntactic extensions.

@@

All other data structures in Redis also follow the semantics similar to
 "List or nothing". Take the case of \mintinline{text}{GET}, which also shares a
 "String or nothing" semantics that should be typed:

@@

Some command may take a variable number of arguments as inputs, and returns more
 than one value as outputs. To illustrate this, consider
 \mintinline{haskell}{sinter} in Hedis:

@@

\textbf{Not all Redis programs can be typechecked} (even if they
 might turn out to be type safe). We opted for type safety rather than
 expressiveness.

@@

Redis has \emph{transactions}, another context for executing commands.
Redis transactions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served \textbf{in the middle}.\footnotemark In contrast, we cannot make such
 a guarantee in the ordinary context, which may destroy the assertions we made
 in types.

@@

We have demonstrated how a DSL with variable bindings could be embedded in types.
With more and more extensions added to the language, Haskell is gradually
 becoming a dependently-typed language,\footnote{Why not be dependently typed? \url{http://stackoverflow.com/questions/12961651/why-not-be-dependently-typed}}
 but it's not that dreadful as many (including us) would have thought.
